Pitfall of Prediction-orienterd Machine Learning Models and Economic Value of Statistical Efficiency in On-farm Precision Experimentation

### 2022-02-19 Writing/manuscript.rmd
results updates (figures, writing)

# /*----------------------------------*/
#' ##  data preparation
# /*----------------------------------*/
#' load results data
est_data <-
  readRDS(here("Shared", "Results", "est_result_ls.rds")) %>%
  rbindlist() %>%
  dplyr::select(model, perform, field_col) %>%
  unnest(perform) %>%
  data.table()
#' rename columns
est_data <- est_data %>%
  .[, .(field_col, model, sim, profit, rmse_train, rmse_cv, rmse_eonr)] %>%
  #---field size---
  .[, field_size := paste0(round(field_col * 72 * 6^2 / 10000, 1), " ha")] %>%
  .[, field_size := factor(field_size, levels = c("9.3 ha", "18.7 ha", "37.3 ha"))] %>%
  #---model name---
  .[model == "brf", model := "BRF"] %>%
  .[model == "rf", model := "RF"] %>%
  .[model == "rf_perfect", model := "RF best"] %>%
  .[model == "lm", model := "LM"] %>%
  .[model == "ser_50", model := "SER"] %>%
  .[, model := factor(model, levels = c("RF", "RF best", "BRF", "LM", "SER"))]
#' mean and sd
mean_data <- est_data %>%
  .[, .(
    profit = mean(profit) %>% round(2),
    profit_sd = sd(profit) %>% round(2),
    rmse_yield = mean(rmse_cv) %>% round(2),
    rmse_yield_sd = sd(rmse_cv) %>% round(2),
    rmse_eonr = mean(rmse_eonr) %>% round(2),
    rmse_eonr_sd = sd(rmse_eonr) %>% round(2)
  ),
  by = c("field_size", "model")
  ] %>%
  .[order(field_size, model), ]

# /*----------------------------------*/
#' ##  create figures and tables
# /*----------------------------------*/
gdata <- est_data
source(here("GitControlled", "Codes", "3_make_figures_tables.R"))
```

@@

+ Traditional vs ML (LM, SER better than RF and BRF)
+ Yield prediction vs EONR prediction
+ Statistical efficiency is money (SER vs LM)

The main purpose of this study is to compare the performance of prediction-oriented ML methods and traditional linear regreression approaches in terms of the profitability of estimated site-specific nitrogen recommendation. Since the true site-specific EONR and maximum profit achievable is never observable for real fields, testing the statistical and economic properties of statistical methods have to rely on simulation analysis where the data generating process is known to the researcher. We conduct MC simualtions for three different field sizes to test the economic performance of linear model OLS, linear model SER, Random Fores, and Boosted Regression Forest, where the true yield follows a quadratic plateau functional form.

We found that while the prediction-oriented ML methods (RF and BRF) perform much better than the traditional methods (LM and SER) in predicting yield level, they perform worse than the traditional methods (LM and SER) in predicting EONR and thus in profitability of site-specific EONR recommendation. SER in particular performs the best in profitability. The economic value of its statistical efficiency over the LM approach is not negligible at <span style = "color: blue;"> Xiafei, put numbers here </span>. Our results provide a cautionary tale for those who place unsubstantiated and blind trust in prediction-oriented ML methods and apply them when the accurate estimation of ceteris paribus causal impacts of the variable of interest is warranted.

@@

In our Monte Carlo simulations, we will test five estimation approches on three different sizes of fields: x ha, y ha, and x ha. In this section, we describe the data generating process, estimation approaches, and model evaluation.

@@

Data were generated at the cell-level and then aggregted up to analysis-unit levle (why). Cell-levle yields were generated following the quadratic-plateau functional form as follows:

$$
\begin{aligned}
y_{i,j} = 
  \begin{cases}
  \alpha_{i,j} + \beta_{i,j} N + \gamma_{i,j} N^2 + \varepsilon_{i,j}, & N < \tau_{i,j} \\
  \eta_{i,j}, & N \geq \tau_{i,j}
  \end{cases}
\end{aligned}
$$

In this formualtion, yield increases as $N_{i,j}$ increaes until $N_{i,j}$ reaches $\tau_{i,j}$, at which yield hits the plateau, $\eta_{i,j}$. The yield level at $N_{i,j}= 0$ is $\alpha_{i,j}$. The rate at which yield increases with repsect to $N_{i,j}$ is governed by $\beta_{i,j}$ and $\gamma_{i,j}$.

Farmers do not observe any of the parameters, but observe the decomposition of the parameters that goven the yield resopnse function. Specifically,

@@

In addition to the covariates, two nuisance covariates that are correlated with eahc of $\alpha_{i,j}$, $\tau_{i,j}$, and $\eta_{i,j}$ are generated: $\phi^{\alpha, 1}_{i,j}$, $\phi^{\alpha, 2}_{i,j}$, $\phi^{\tau, 1}_{i,j}$, $\phi^{\tau, 2}_{i,j}$, $\phi^{\eta, 1}_{i,j}$, $\phi^{\eta, 2}_{i,j}$. We denote these variables as $X^2_{i,j}$. These variables are nuisance in the sense that they provide no additional information about the yield response functions once $X^1_{i,j}$ are included as covariates. Since they are correlated with $X^1_{i,j}$, the inclusion of $X^2_{i,j}$ would interfere with accurate identification of the $X^1_{i,j}$. We denote $X^1_{i,j}$ and $X^2_{i,j}$ collectively as $X_{i,j}$. Once the cell-level variables are generated, true economically optimal can be found by solving the profit maximization problem. This process is repeated 1000 times to create 1000 datasets. See Appendix \@ref(parameters) for maps of some of the covariates and true EONR for a single simulation round as an example. The cell level data were then aggregated up to the analysis unit level data: $\{y_i, X_i\}$.

@@

**Approach 1**: Linear Model OLS (Hereafter, LM)

The LM approach assumes a quadratic yield response function:

@@

The econometic model for the SER approach follows that of the LM approach except for the error term.

@@

where $\lambda$ is scaler that reflects the degree of spatial dependence, $W$ is the user-defined weight matrix, and $\mu$ is the idiosynctaric error term that is not spatially correlated. Estimation via the spatial error model takes into account the spatial dependency of the error term and thus statistically more  efficient than the LM approach. The _spatialreg_ package in R was used to estimate the model (cite).

@@

Unlike the LM and SER approaches, it does not assume any particular functional relationships between the dependent vairable and the covaraites. Random Forest consists of ensembles of trees. In each tree, the train data is split into a number of leaves based on the covirate values and all the observations belonging to the same leaf share the same yield estimate. Unlike a single classification and regression tree (CART), RF tends to avoid overfitting thanks to the averaging of estimates from the individual trees. The RF approach uses all the variables $(X_{i})$ as covariates.

@@

While RF builds individual trees completely independent of one another, BRF build trees in a way that focuses relatively more on imroving the parts of the data that are not well explained in the previous sequence of trees. Consequently, BRF tends to perform better than RF in predicting yield. However, its use in the context of site-specific input management is limited compared to RF at the moment. The BRF approach uses all the covaraites in $X$ like the LM, SER, and RF approaches. The _grf_ package in R was used to run the RF, RF$_{best}$, and BRF estimations (cite). Hyperparameters were tuned using cross-validation.

@@

$$
\begin{aligned}
RMSE = \sqrt{\frac{1}{n} \sum_{i=1}^{n} (\hat{y}_i - y_i)^2}
\end{aligned}
$$
where $y_i$ is the true yield of location $i$ from applying the trial N rate, and $\hat{y}_i$ is the predicted yield of the same location by a certain model. The total number of locations for that simulated trial field is $n$.

@@

$$
\begin{aligned}
RMSE = \sqrt{\frac{1}{n} \sum_{i=1}^{n} (\hat{EONR}_i - EONR_i)^2}
\end{aligned}
$$
where $EONR_i$ is the true economically optimal nitrogen rate of location $i$, and $\hat{EONR}_i$ is the predicted EONR for location $i$ by a certain model. The total number of locations for that simulated trial field is $n$.

@@

## Main point 1:
Despite machine learning models perform better in yield predicting, their EONR prediction is poor.

The performances of different models in out-of-sample yield prediction, EONR prediction, and EONR profitability over 1,000 simulations are displayed in Figure \@ref(fig:comb-boxplot-large) for the large trial field (37.3 ha) scenario.

- Indeed, the simulation results showed the machine learning models perform better than traditional regression models in yield predicting. On average, the predicted yields' RMSE of RF (`r mean_data[field_size=="37.3 ha"&model=="RF", rmse_yield] %>% round(2)` kg ha$^{-1}$) and BRF (`r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_yield] %>% round(2)` kg ha$^{-1}$) models are significantly smaller than that of the LM (`r mean_data[field_size=="37.3 ha"&model=="LM", rmse_yield] %>% round(2)` kg ha$^{-1}$) or SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_yield] %>% round(2)` kg ha$^{-1}$) model. Those findings are consistent with existing literature (**citations**).
- However, the better yield prediction of machine learning models does not necessarily translate into better EONR prediction. The predicted EONR's RMSE of the RF model (`r mean_data[field_size=="37.3 ha"&model=="RF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) is much larger than the LM (`r mean_data[field_size=="37.3 ha"&model=="LM", rmse_eonr] %>% round(2)` kg ha$^{-1}$) or SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_eonr] %>% round(2)` kg ha$^{-1}$) model, meaning the RF model generates much inaccurate EONR predictions, despite its more accurate yield predictions, than LM or SER model. BRF model's EONR prediction is much better than RF model, whose RMSE (`r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) is only slightly smaller than the LM model. But it is still significantly larger than the SER model.
- Finally, the less accurate EONR predictions by machine learning models lead to lower profits. The average profit of RF model ($\$$`r mean_data[field_size=="37.3 ha"&model=="RF", profit] %>% round(2)` ha$^{-1}$) is extremely low. The BRF model profit ($\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$) is much higher than RF, but still significantly lower than the basic LM model ($\$$`r mean_data[field_size=="37.3 ha"&model=="LM", profit] %>% round(2)` ha$^{-1}$). The SER model profit is as high as $\$$`r mean_data[field_size=="37.3 ha"&model=="SER", profit] %>% round(2)` ha$^{-1}$.

@@

## Main point 2:
The model performances are generally robust to field sizes. But we also found that machine learning models' performances are less affected by field size reduction.

The simulation results for medium (18.7 ha) and small (9.3 ha) trial field scenarios are displayed in Figure \@ref(fig:comb-boxplot-medium) and \@ref(fig:comb-boxplot-small).

- The RF model still has better yield prediction while worse EONR prediction and profit than the LM and SER models.
- The BRF model outperforms LM model in EONR prediction and profit in medium and small trial fields. 
- Though the BRF model still cannot beat SER model in smaller fields, the gap between BRF and SER shrink as field size reduces. For the small field (9.3 ha), BRF's predicted EONR RMSE (`r mean_data[field_size=="9.3 ha"&model=="BRF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) is almost as small as that of the SER model (`r mean_data[field_size=="9.3 ha"&model=="SER", rmse_eonr] %>% round(2)` kg ha$^{-1}$), and the profit gap between the BRF model (`r mean_data[field_size=="9.3 ha"&model=="BRF", profit] %>% round(2)` kg ha$^{-1}$) and the SER model (`r mean_data[field_size=="9.3 ha"&model=="BRF", profit] %>% round(2)` kg ha$^{-1}$) reduces to only about two thirds of the large field (37.3 ha) scenario.

So, the better economic performances of traditional regression models require larger trial field sizes. Machine learning models' performances are less sensitive to field sizes. At the current prevailing on-farm experimental field sizes, traditional regression models perform well. But if the trial fields are really small, machine learning models (especially BRF) will be more suitable.

## Main point 3:
EONR prediction and profit is not perfectly one-on-one corresponding.

@@

## Main point 4:
RF model is bad.

- Even if we "cheat" and feed RF model with the best data, its profit is still only $\$$`r mean_data[field_size=="37.3 ha"&model=="RF best", profit] %>% round(2)` ha$^{-1}$ 
If we estimate RF model with the best data, its RMSE will be further smaller (`r mean_data[field_size=="37.3 ha"&model=="RF best", rmse_yield] %>% round(2)` kg ha$^{-1}$).

## Main point 5:
LM vs. SER: Statistical efficiency is money.

@@

```{r comb-boxplot-large, fig.cap="The performances of different models, large field.", echo=FALSE, fig.width=6}
comb_boxplot_large
```

```{r comb-boxplot-medium, fig.cap="The performances of different models, medium field.", echo=FALSE, fig.width=6}
comb_boxplot_medium
```

```{r comb-boxplot-small, fig.cap="The performances of different models, small field.", echo=FALSE, fig.width=6}
comb_boxplot_small
```

>>>>

# /*----------------------------------*/
#' ##  data preparation
# /*----------------------------------*/
#' load results data
est_data <-
  readRDS(here("Shared", "Results", "est_result_ls.rds")) %>%
  rbindlist() %>%
  dplyr::select(model, perform, field_col) %>%
  unnest(perform) %>%
  data.table()
#' rename columns
est_data <- est_data %>%
  .[, .(field_col, model, sim, profit, rmse_train, rmse_cv, rmse_eonr)] %>%
  #---field size---
  .[, field_size := paste0(round(field_col * 72 * 6^2 / 10000, 1), " ha")] %>%
  .[, field_size := factor(field_size, levels = c("9.3 ha", "18.7 ha", "37.3 ha"))] %>%
  #---model name---
  .[model == "brf", model := "BRF"] %>%
  .[model == "rf", model := "RF"] %>%
  .[model == "rf_perfect", model := "RF_b"] %>%
  .[model == "lm", model := "OLS"] %>%
  .[model == "ser_50", model := "SER"] %>%
  .[, model := factor(model, levels = c("RF", "RF_b", "BRF", "OLS", "SER"))]
#' mean and sd
mean_data <- est_data %>%
  .[, .(
    profit = mean(profit) %>% round(2),
    profit_sd = sd(profit) %>% round(2),
    rmse_yield = mean(rmse_cv) %>% round(2),
    rmse_yield_sd = sd(rmse_cv) %>% round(2),
    rmse_eonr = mean(rmse_eonr) %>% round(2),
    rmse_eonr_sd = sd(rmse_eonr) %>% round(2)
  ),
  by = c("field_size", "model")
  ] %>%
  .[order(field_size, model), ]
#' load illustration data (single simulation)
illus_data <-
  readRDS(here("Shared", "Results", "illus_data.rds"))

# /*----------------------------------*/
#' ##  create figures and tables
# /*----------------------------------*/
source(here("GitControlled", "Codes", "3_make_figures_tables.R"))
```

@@

+ Traditional vs ML (OLS, SER better than RF and BRF)
+ Yield prediction vs EONR prediction
+ Statistical efficiency is money (SER vs OLS)

The main purpose of this study is to compare the performance of prediction-oriented ML methods and traditional linear regression approaches in terms of the profitability of estimated site-specific nitrogen recommendation. Since the true site-specific EONR and maximum profit achievable is never observable for real fields, testing the statistical and economic properties of statistical methods have to rely on simulation analysis where the data generating process is known to the researcher. We conduct MC simulations for three different field sizes to test the economic performance of linear model OLS, linear model SER, Random Fores, and Boosted Regression Forest, where the true yield follows a quadratic plateau functional form.

We found that while the prediction-oriented ML methods (RF and BRF) perform much better than the traditional methods (OLS and SER) in predicting yield level, they perform worse than the traditional methods (OLS and SER) in predicting EONR and thus in profitability of site-specific EONR recommendation. SER in particular performs the best in profitability. The economic value of its statistical efficiency over the OLS approach is not negligible at <span style = "color: blue;"> Xiafei, put numbers here </span>. Our results provide a cautionary tale for those who place unsubstantiated and blind trust in prediction-oriented ML methods and apply them when the accurate estimation of ceteris paribus causal impacts of the variable of interest is warranted.

@@

In our Monte Carlo simulations, we will test five estimation approaches on three different sizes of fields: x ha, y ha, and x ha. In this section, we describe the data generating process, estimation approaches, and model evaluation.

@@

Data were generated at the cell-level and then aggregated up to analysis-unit level (why). Cell-level yields were generated following the quadratic-plateau functional form as follows:

$$
\begin{aligned}
y_{i,j} = 
  \begin{cases}
  \alpha_{i,j} + \beta_{i,j} N + \gamma_{i,j} N^2 + \varepsilon_{i,j}, & N < \tau_{i,j} \\
  \eta_{i,j} + \varepsilon_{i,j}, & N \geq \tau_{i,j}
  \end{cases}
\end{aligned}
$$

In this formulation, yield increases as $N_{i,j}$ increase until $N_{i,j}$ reaches $\tau_{i,j}$, at which yield hits the plateau, $\eta_{i,j}$. The yield level at $N_{i,j}= 0$ is $\alpha_{i,j}$. The rate at which yield increases with respect to $N_{i,j}$ is governed by $\beta_{i,j}$ and $\gamma_{i,j}$.

Farmers do not observe any of the parameters, but observe the decomposition of the parameters that given the yield response function. Specifically,

@@

In addition to the covariates, two nuisance covariates that are correlated with each of $\alpha_{i,j}$, $\tau_{i,j}$, and $\eta_{i,j}$ are generated: $\phi^{\alpha, 1}_{i,j}$, $\phi^{\alpha, 2}_{i,j}$, $\phi^{\tau, 1}_{i,j}$, $\phi^{\tau, 2}_{i,j}$, $\phi^{\eta, 1}_{i,j}$, $\phi^{\eta, 2}_{i,j}$. We denote these variables as $X^2_{i,j}$. These variables are nuisance in the sense that they provide no additional information about the yield response functions once $X^1_{i,j}$ are included as covariates. Since they are correlated with $X^1_{i,j}$, the inclusion of $X^2_{i,j}$ would interfere with accurate identification of the $X^1_{i,j}$. We denote $X^1_{i,j}$ and $X^2_{i,j}$ collectively as $X_{i,j}$. Once the cell-level variables are generated, true economically optimal can be found by solving the profit maximization problem. This process is repeated 1000 times to create 1000 datasets. See Appendix \@ref(parameters) for maps of some of the covariates and true EONR for a single simulation round as an example. The cell level data were then aggregated up to the analysis unit level data: $\{y_i, X_i\}$.

@@

**Approach 1**: Linear Model OLS (Hereafter, OLS)

The OLS approach assumes a quadratic yield response function:

@@

The econometic model for the SER approach follows that of the OLS approach except for the error term.

@@

where $\lambda$ is scaler that reflects the degree of spatial dependence, $W$ is the user-defined weight matrix, and $\mu$ is the idiosynctaric error term that is not spatially correlated. Estimation via the spatial error model takes into account the spatial dependency of the error term and thus statistically more  efficient than the OLS approach. The _spatialreg_ package in R was used to estimate the model (cite).

@@

Unlike the OLS and SER approaches, it does not assume any particular functional relationships between the dependent vairable and the covaraites. Random Forest consists of ensembles of trees. In each tree, the train data is split into a number of leaves based on the covirate values and all the observations belonging to the same leaf share the same yield estimate. Unlike a single classification and regression tree (CART), RF tends to avoid overfitting thanks to the averaging of estimates from the individual trees. The RF approach uses all the variables $(X_{i})$ as covariates.

@@

While RF builds individual trees completely independent of one another, BRF build trees in a way that focuses relatively more on imroving the parts of the data that are not well explained in the previous sequence of trees. Consequently, BRF tends to perform better than RF in predicting yield. However, its use in the context of site-specific input management is limited compared to RF at the moment. The BRF approach uses all the covaraites in $X$ like the OLS, SER, and RF approaches. The _grf_ package in R was used to run the RF, RF$_{best}$, and BRF estimations (cite). Hyperparameters were tuned using cross-validation.

@@

$$
\begin{aligned}
RMSE_{y} = \sqrt{\frac{1}{n} \sum_{i=1}^{n} (\hat{y}_i - y_i)^2}
\end{aligned}
$$
where $y_i$ is the true yield of location $i$ from applying the trial N rate, and $\hat{y}_i$ is the predicted yield of the same location by a certain model. The total number of locations for that simulated trial field is $n$.

@@

$$
\begin{aligned}
RMSE_{EONR} = \sqrt{\frac{1}{n} \sum_{i=1}^{n} (\hat{EONR}_i - EONR_i)^2}
\end{aligned}
$$
where $EONR_i$ is the true economically optimal nitrogen rate of location $i$, and $\hat{EONR}_i$ is the predicted EONR for location $i$ by a certain model. The total number of locations for that simulated trial field is $n$.

@@

## EONR prediction

The performances of machine learning and traditional regression models from 1,000 simulations were compared in Figure \@ref(fig:comb-boxplot-all). Three performance measurements: (1) out-of-sample yield prediction, (2) out-of-sample EONR prediction, and (3) profit resultant from the predicted EONR.

Table of winner counts.

Look at the large field (37.3 ha) scenario in panel (A) of Figure \@ref(fig:comb-boxplot-all).

- Indeed, the simulation results showed that machine learning models have better yield predictions than traditional regression models. On average, the out-of-sample predicted yields' RMSE of RF (`r mean_data[field_size=="37.3 ha"&model=="RF", rmse_yield] %>% round(2)` kg ha$^{-1}$) and BRF (`r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_yield] %>% round(2)` kg ha$^{-1}$) models were significantly smaller than that of OLS (`r mean_data[field_size=="37.3 ha"&model=="OLS", rmse_yield] %>% round(2)` kg ha$^{-1}$) or SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_yield] %>% round(2)` kg ha$^{-1}$) model. Those results are consistent with existing literature (**citations**).
- However, the better yield prediction of machine learning models does not translate into better EONR prediction. The average RMSE of out-of-sample predicted EONR of RF (`r mean_data[field_size=="37.3 ha"&model=="RF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) was much larger than that of OLS (`r mean_data[field_size=="37.3 ha"&model=="OLS", rmse_eonr] %>% round(2)` kg ha$^{-1}$) or SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_eonr] %>% round(2)` kg ha$^{-1}$) model. BRF model's EONR prediction (RMSE `r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) was better than RF model, which was similar to OLS model, but was still significantly worse than SER model. Those results showed that, despite machine learning models have better yield prediction, their EONR prediction is worse than traditional regression models.
- Ultimately, the worse EONR prediction of machine learning models resulted in lower production profit compared to the traditional regression models. The 1,000-simulation average profit of RF ($\$$`r mean_data[field_size=="37.3 ha"&model=="RF", profit] %>% round(2)` ha$^{-1}$) or BRF ($\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$) model is significantly lower than that of OLS ($\$$`r mean_data[field_size=="37.3 ha"&model=="OLS", profit] %>% round(2)` ha$^{-1}$) or SER ($\$$`r mean_data[field_size=="37.3 ha"&model=="SER", profit] %>% round(2)` ha$^{-1}$) model.

## RF model is bad

- Within the machine learning models, the RF model performs especially poor in EONR prediction. Its EONR prediction RMSE was much larger than BRF model, and its associated profit was extremely low. 
- Even if we "cheat" and feed RF model with the best possible data (the true yield response parameters), its EONR prediction (RMSE `r mean_data[field_size=="37.3 ha"&model=="RF_b", rmse_eonr] %>% round(2)` kg ha$^{-1}$) and profit performance ($\$$`r mean_data[field_size=="37.3 ha"&model=="RF_b", profit] %>% round(2)` ha$^{-1}$) were still slightly worse than BRF model ($\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$) with observed data. 
- Note that RF is currently a very popular machine learning method used by many agricultural studies. Our simulation results showed that although RF may be OK for yield prediction, it is terrible in EONR prediction, and will cause big economic loss if using it in decision making. Even after spending great efforts (and costs) to obtain the perfect information, using RF model still won't achieve good economic performance.

## Field sizes

Figure \@ref(fig:comb-boxplot-all) panels (B) and (C) showed the simulation results for medium (18.7 ha) and small (9.3 ha) fields.

- The result pattern of model performances was generally robust to field sizes. For any sized field, the machine learning models still have better yield predictions while worse economic performances than traditional regression models. 
- But we do notice that machine learning models' economic performances catch up when field size decreases. Especially, BRF model outperformed OLS model in EONR prediction and profit performance in small and medium fields. Although BRF model still cannot win SER in profit performance, its profit gap between SER reduced from $\$$`r (mean_data[field_size=="37.3 ha"&model=="SER", profit] - mean_data[field_size=="37.3 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ in large field to $\$$`r (mean_data[field_size=="18.7 ha"&model=="SER", profit] - mean_data[field_size=="18.7 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ in medium field and $\$$`r (mean_data[field_size=="9.3 ha"&model=="SER", profit] - mean_data[field_size=="9.3 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ in small field.
- The results may suggest machine learning models (especially BRF) are more desirable in small fields' EONR predictions. But under the context of current farming practice, most production fields are larger than the smallest field (9.3 ha) scenario of our simulation, SER model is economically best option.

## Illustrative explanation

- One simulation example (cherry picking, similar to the mean pattern)

- One location's yield response curves

- Treatment effects

short summary:

@@

## OLS vs. SER: Statistical efficiency is money.

## EONR prediction and profit is not perfectly one-to-one corresponding. (perhaps too much; remove this point)

@@

illustrative figure:

@@

```{r comb-boxplot-all, fig.cap="The estimation performances of machine learning models (RF, RF_b, BRF) and traditional regression models (OLS, SER) over 1,000 simulations for: (A) large field (37.3 ha), (B) medium field (18.7 ha), and (C) small field (9.3 ha). The performance measurements include: (1) out-of-sample yield prediction RMSE, (2) out-of-sample EONR prediction RMSE, and (3) profit resultant from the predicted EONR.", echo=FALSE, fig.height=8.5, fig.width=7, cache=FALSE}
(comb_boxplot_large + ggtitle("(A) large field")) / (comb_boxplot_medium + ggtitle("(B) medium field")) / (comb_boxplot_small + ggtitle("(C) small field"))
```

```{r single-simu-yield, fig.cap="Example simulation, yield.", fig.width=6, fig.height=7.5, echo=FALSE, cache=FALSE}
single_simu_yield
```

```{r single-simu-EONR, fig.cap="Example simulation, EONR", fig.width=6, fig.height=7.5, echo=FALSE, cache=FALSE}
single_simu_EONR
```
